Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
correct hyphenation.
adding comment.
adding "only".

In BDD, all behavior should be documented, together with some testable
\emph{evidence} for that behavior.  Most existing BDD tools use
\emph{code examples} as evidence for behavior.
Hspec, a BDD tool for Haskell inspired by RSpec, supports
both code examples and \emph{properties} as evidence.
It can verify examples and test properties, and it can create an
informal specification document from that.

\begin{quote}
    \emph{kazu: we should talk about Python's doctest,
    Haskell's doctest and Haddock here and put
    citation on them.}
\end{quote}

@@

@@

\noindent Note that the $\hookleftarrow$ symbol denotes that two lines are actually written in a single line. If a default type is not suitable, expression type--signatures can be specified for each parameter:

>>>>

\begin{quote}
    \emph{kazu: I would like to exchange 2nd sentence and 3rd sentence:}

BDD includes TDD, but with a terminology and mindset shifted towards
specification instead of testing. In BDD, specifications can be used
for automatic testing.  BDD also includes other software development
methods, such as automatic test discovery and continuous
integration~\cite{ci}.  BDD-style TDD has been pioneered by
RSpec~\cite{rspec}.  In this paper, we explore how to apply the TDD
aspect of BDD to Haskell.

\end{quote}

In BDD, all behavior should be documented, together with some testable
\emph{evidence} for that behavior.  Most existing BDD tools only use
\emph{code examples} as evidence for behavior.
Hspec, a BDD tool for Haskell inspired by RSpec, supports
both code examples and \emph{properties} as evidence.
It can verify examples and test properties, and it can create an
informal specification document from that.

@@

\begin{quote}
    \emph{kazu: I would like to change blocks above (from ``We made two ...'') with:}

Hspec is thus useful for code documentation but we observed that parts
of a specification can be useful as user documentation. We pay attention
to Python's Doctest~\cite{doctest} for this purpose.
Doctest is not commonly described as a BDD tool, but we think
it can be used for BDD.
There is Haskell version of Doctest\footnote{%
http://hackage.haskell.org/package/doctest} coped with Haddock~\cite{haddock},
standard documentation mechanism for Haskell.
It extracts \emph{interactive examples} in Haddock comments and
verify them automatically.

We will show how to use Doctest and Hspec in combination to design,
document and test Haskell code.
Both, Doctest and Hspec are missing some features.  So we extend them
as needed.  In particular, our contributions are:
\end{quote}

@@

\noindent Note that the $\hookleftarrow$ symbol denotes that two lines are actually written in a single line. If a default type is not suitable, expression type-signatures can be specified for each parameter:
